IFC Inside: A General Approach to Retrofitting Languages with Dynamic Information Flow Control

### 2015-01-15 paper/real.tex
reviewer 2 and 3 (first point): isolation is language-specific

In this section, we describe two JavaScript IFC implementations
building on the theoretical foundations of this work.
%
Furthermore, we consider how our formalism could be applied to the C
programming language
and connect it to a previous IFC system for
Haskell.
%
%% The goal of this section is to show the flexibility of the embedding in settings with
%% vastly different properties and discuss the
%% semantic gap that must be overcome to apply our formalism
%% to other systems.
%
%% Two of the systems we describe have been implemented: the Haskell
%% system~\cite{lio} and the COWL~\cite{swapi} system; we leave the
%% implementation of the IFC system for C to future work.

>>>>

Our approach can be used to retrofit any language for which we
can achieve isolation with information flow control.
%
Unfortunately, controlling the external effects of a real-world
language, as to achieve isolation, is language-specific and varies
from one language to another.\footnote{
  Though we apply our framework to several real-world languages, it is
  conceivable that there are languages for which isolation cannot be
  easily achieved.
}
%
Indeed, even for a single language (e.g., JavaScript), how one
achieves isolation may vary according to the language runtime or
embedding (e.g., server and browser).
%

In this section, we describe several implementations and their
approaches to isolation.
%
In particular, we describe two JavaScript IFC implementations
building on the theoretical foundations of this work.
%
Then, we consider how our formalism could be applied to the C
programming language and connect it to a previous IFC system for
Haskell.
%

%% The goal of this section is to show the flexibility of the embedding in settings with
%% vastly different properties and discuss the
%% semantic gap that must be overcome to apply our formalism
%% to other systems.
%
%% Two of the systems we describe have been implemented: the Haskell
%% system~\cite{lio} and the COWL~\cite{swapi} system; we leave the
%% implementation of the IFC system for C to future work.
